\speculake: Hiding Malware in Speculative Execution

### 2018-05-09 paper/paper.tex
add paper number
minor front matter fixes

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Paper \#XXX} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

@@

\keywords{Malware; Covert Channel; Weird Machines; TK} % TODO: replace with your keywords

>>>>

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Paper \#629} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

@@

\keywords{Malware; Covert Channel; Weird Machines; Spectre} % TODO: replace with your keywords
